OSF management

### 2021-01-05 osf/comps/data/exp-materials/norming/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

---
title: "Norming results"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the results from the norming study.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Dataset & Materials")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "Materials/Norming results") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

---
title: "Norming study"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the `images/` used in the norming study and the `results/` of the study (i.e. the typicality ratings for each image/object for each participant).

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "exp-materials/norming") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

### 2021-01-05 osf/manage-osf.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Dataset & Materials")
```

@@

We can knit the readme files (they are GitHub documents, i.e. `.Rmd` files that are converted to `.md` files upon knitting) by running `osf/knit-all.R`.

------
**NOTE**

For some reason I can't get this file to knit the other Rmd files when knitted (I get an error).
So for now we need to manually run the `osf/knit-all.R` script before uploading files to OSF.
I asked on StackOverflow how to fix this: <https://stackoverflow.com/q/65505119/2804314>.

------

@@

```{r readmes}
# A loop would be better
osf_upload(data_comp, path = "./osf/comps/dataset/README.md", conflicts = "overwrite", verbose = T)

@@

materials <- data_comp_files %>% filter(name == "Materials")
osf_upload(materials, path = "./osf/comps/dataset/materials/README.md", conflicts = "overwrite", verbose = T)

raw <- data_comp_files %>% filter(name == "Raw data")
osf_upload(raw, path = "./osf/comps/dataset/raw/README.md", conflicts = "overwrite", verbose = T)

tgs <- data_comp_files %>% filter(name == "TextGrids")
osf_upload(tgs, path = "./osf/comps/dataset/textgrids/README.md", conflicts = "overwrite", verbose = T)
```

>>>>

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

@@

We can knit the readme files (they are GitHub documents, i.e. `.Rmd` files that are converted to `.md` files upon knitting).

```{r knit-all, message=FALSE, warning=FALSE}
files <- list.files("./osf/comps/data", pattern = "[.]Rmd$", recursive = T, full.names = T)

for (f in files) {
  xfun::Rscript_call(rmarkdown::render, list(f))
}
```

@@

```{r readmes}
# A loop would be better
osf_upload(data_comp, path = "./osf/comps/data/README.md", conflicts = "overwrite", verbose = T)

@@

# data/data
raw <- data_comp_files %>% filter(name == "data")

osf_rm(osf_ls_files(data_comp, "data", pattern = "README.md"), check = FALSE)
osf_upload(raw, path = "./osf/comps/data/data/README.md", conflicts = "overwrite", verbose = T)

# data/exp-materials
materials <- data_comp_files %>% filter(name == "exp-materials")

osf_rm(osf_ls_files(data_comp, "exp-materials", pattern = "README.md"), check = FALSE)
osf_upload(materials, path = "./osf/comps/data/exp-materials/README.md", conflicts = "overwrite", verbose = T)

# data/exp-materials/norming
osf_rm(osf_ls_files(data_comp, "exp-materials/norming", pattern = "README.md"), check = FALSE)
osf_upload(osf_ls_files(data_comp, "exp-materials", pattern = "norming"), path = "./osf/comps/data/exp-materials/norming/README.md", conflicts = "overwrite", verbose = T)

# data/exp-materials/experiment
osf_rm(osf_ls_files(data_comp, "exp-materials/experiment", pattern = "README.md"), check = FALSE)
osf_upload(osf_ls_files(data_comp, "exp-materials", pattern = "experiment"), path = "./osf/comps/data/exp-materials/experiment/README.md", conflicts = "overwrite", verbose = T)
```
